Robust Bayesian Analysis of Causal Inference Problems

### 2024-03-22 JASA-template.tex
Mention true value.
Small updates.

\paragraph{Results}
\Cref{tab:causal} shows the results of estimating the causal effect $\beta_T$. 
As we perform a sensitivity analysis,
our method gives an interval estimate for the causal effect and we show
that in two different rows where the first row gives the lower bound
and the second row gives the upper bound. We notice that our method is 
somewhat in agreement with the other methods but much more consistent
in terms of estimating the treatment effect. However, this is not the
case for other methods and sometimes those methods produce extreme 
values. This can be observed in \cref{fig:comp:trt} as well. Here, the true 
value is represented by the straight line for $\beta_T = 4$.

>>>>

\paragraph{Results}
\Cref{tab:causal} shows the results of estimating the causal effect $\beta_T$
For reference, recall the true value is $\beta_T=4$. 
As we perform a sensitivity analysis,
our method gives an interval estimate for the causal effect:
the first row gives the lower bound
and the second row gives the upper bound. We notice that our method is 
somewhat in agreement with the other methods but is more consistent
in terms of estimating the treatment effect. However, this is not the
case for other methods and sometimes those methods produce extreme 
values. This can be observed in \cref{fig:comp:trt} as well. Here, the true 
value is represented by the straight line for $\beta_T = 4$.
